% OA TUTORS - 11+ Curriculum
% Extension Activity Template
% Website: https://oatutors.co.uk/

\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{tcolorbox}
\usepackage{enumitem}

% Page setup
\geometry{margin=2cm}
\pagestyle{fancy}

% Colors
\definecolor{oablue}{RGB}{0,51,102}
\definecolor{oagray}{RGB}{128,128,128}
\definecolor{oagreen}{RGB}{34,139,34}

% Header and footer setup
\fancyhf{}
\fancyhead[L]{\textcolor{oagreen}{\textbf{EXTENSION}}}
\fancyhead[C]{\textcolor{oablue}{11+ Mathematics - Extension Activity}}
\fancyhead[R]{\textcolor{oablue}{Lesson 06}}
\fancyfoot[C]{\textcolor{oagray}{\thepage}}
\fancyfoot[R]{\textcolor{oagray}{https://oatutors.co.uk/}}

% Custom boxes
\newtcolorbox{challenge}{
    colback=green!10!white,
    colframe=oagreen,
    title=Super Challenge!
}

\newtcolorbox{investigate}{
    colback=blue!5!white,
    colframe=blue!50!black,
    title=Investigation
}

\newtcolorbox{creative}{
    colback=purple!5!white,
    colframe=purple!50!black,
    title=Creative Task
}

% Document starts here
\begin{document}

\title{\textcolor{oagreen}{\Huge Extension Activities} \\ 
       \textcolor{oablue}{\Large Lesson 06: Rounding}}
\author{\textcolor{oablue}{OA Tutors} \\ 
        \textcolor{oagray}{https://oatutors.co.uk/}}
\date{\textcolor{oagray}{\today}}

\maketitle

\begin{challenge}
\textbf{Well done!} You've mastered the basics of this topic. \\
These activities will stretch your thinking and help you explore the topic further.

\textbf{Choose from:} Problem-solving challenges, investigations, or creative tasks.
\end{challenge}

\section{Problem-Solving Challenges}

\subsection{Challenge 1: [CHALLENGE_TITLE_1]}
\textbf{Difficulty:} ⭐⭐⭐

[CHALLENGE_DESCRIPTION_1]

\textbf{Your task:}
\begin{enumerate}
    \item [TASK_STEP_1]
    \item [TASK_STEP_2]
    \item [TASK_STEP_3]
\end{enumerate}

\textbf{Thinking space:}

\vspace{4cm}

\subsection{Challenge 2: [CHALLENGE_TITLE_2]}
\textbf{Difficulty:} ⭐⭐⭐⭐

[CHALLENGE_DESCRIPTION_2]

\vspace{4cm}

\section{Investigations}

\begin{investigate}
\textbf{Research Question:} [RESEARCH_QUESTION]

\textbf{What you need to find out:}
\begin{itemize}
    \item [INVESTIGATION_POINT_1]
    \item [INVESTIGATION_POINT_2]
    \item [INVESTIGATION_POINT_3]
\end{itemize}

\textbf{How to investigate:}
\begin{enumerate}
    \item [METHOD_STEP_1]
    \item [METHOD_STEP_2]
    \item [METHOD_STEP_3]
\end{enumerate}
\end{investigate}

\textbf{Record your findings:}

\vspace{5cm}

\textbf{What patterns did you notice?}

\vspace{3cm}

\section{Creative Tasks}

\begin{creative}
Choose one of these creative challenges:

\textbf{Option A: [CREATIVE_OPTION_A]}
\begin{itemize}
    \item [CREATIVE_TASK_A]
\end{itemize}

\textbf{Option B: [CREATIVE_OPTION_B]}
\begin{itemize}
    \item [CREATIVE_TASK_B]
\end{itemize}

\textbf{Option C: [CREATIVE_OPTION_C]}
\begin{itemize}
    \item [CREATIVE_TASK_C]
\end{itemize}
\end{creative}

\section{Going Further}

\subsection{Real-World Applications}
[REAL_WORLD_CONNECTION]

\subsection{Cross-Curricular Links}
\begin{itemize}
    \item \textbf{Science:} [SCIENCE_LINK]
    \item \textbf{History:} [HISTORY_LINK] 
    \item \textbf{Art:} [ART_LINK]
\end{itemize}

\subsection{Further Reading}
\begin{itemize}
    \item [BOOK_RECOMMENDATION_1]
    \item [WEBSITE_RECOMMENDATION]
    \item [ACTIVITY_SUGGESTION]
\end{itemize}

\section{Reflection}

\textbf{What was the most interesting thing you discovered?}

\vspace{2cm}

\textbf{What would you like to explore further?}

\vspace{2cm}

\textbf{How could you use this knowledge in other subjects?}

\vspace{2cm}

\vfill
\begin{center}
\textcolor{oagray}{\small \copyright\ 2025 OA Tutors. All rights reserved. | https://oatutors.co.uk/}
\end{center}

\end{document}